### 2016-01-25 format.Rmd
ENH:  More.

---
output:
  pdf_document:
    fig_caption: true
    latex_engine: xelatex
    keep_tex: yes
header-includes:
   - \usepackage{booktabs}
   - \usepackage[font={small},labelfont=bf,labelsep=colon]{caption}
   - \linespread{1.5}
   - \usepackage[compact]{titlesec}
   - \usepackage{enumitem}
   - \usepackage{tikz}
   - \def\checkmark{\tikz\fill[scale=0.4](0,.35) -- (.25,0) -- (1,.7) -- (.25,.15) -- cycle;}
   - \setlist{nolistsep}
   - \titlespacing{\section}{2pt}{*0}{*0}
   - \titlespacing{\subsection}{2pt}{*0}{*0}
   - \titlespacing{\subsubsection}{2pt}{*0}{*0}
   - \setlength{\parskip}{3pt}
bibliography: references.bib
csl: national-science-foundation-grant-proposals.csl
fontsize: 11pt
mainfont: Georgia
geometry: margin=1.0in
---

>>>>

---
output:
  word_document:
    fig_caption: true
  pdf_document:
    fig_caption: true
    latex_engine: xelatex
    keep_tex: yes
header-includes:
   - \usepackage{booktabs}
   - \usepackage[font={small},labelfont=bf,labelsep=colon]{caption}
   - \linespread{1.5}
   - \usepackage[compact]{titlesec}
   - \usepackage{enumitem}
   - \usepackage{tikz}
   - \def\checkmark{\tikz\fill[scale=0.4](0,.35) -- (.25,0) -- (1,.7) -- (.25,.15) -- cycle;}
   - \setlist{nolistsep}
   - \titlespacing{\section}{2pt}{*0}{*0}
   - \titlespacing{\subsection}{2pt}{*0}{*0}
   - \titlespacing{\subsubsection}{2pt}{*0}{*0}
   - \setlength{\parskip}{3pt}
bibliography: references.bib
csl: national-science-foundation-grant-proposals.csl
fontsize: 11pt
mainfont: Georgia
geometry: margin=1.0in
---

### 2016-01-25 methods.Rmd
ENH:  More.

@@

Another versatile technique that has acheieved much success

@@

>>>>

<!--

* Importance of machine learning in medical image analysis
    * give examples
    * (tools) support vector machines
    * (tools) neural networks
    * (apps)
    * Random forests
        * MS lesion detection (Geremeria 2011)
        * Brain tumor segmentation (BRATS 2012 and BRATS 2013)
        * Tustison 2015 (importance of feature images)
        * Pustina 2016

* Overview of protocol
    * Preprocess all images
        * Denoise
        * N4 bias correction
    * Create Stage 1 feature images
    * Use those as input to the first stage RF model to get RF voting maps
        * CSF
        * GM
        * WM
        * Deep GM
        * Brain stem
        * Cerebellum
        * WMHs
    * Use RF voting maps as priors for antsAtroposN4.sh to perform Bayesian-based
      segmentation with an additional Markov random field prior to promote spatial
      smoothness of the labels.
    * Use Stage 1 feature images + RF voting maps + antsAtroposN4.sh posteriors as
      Stage 2 feature images.
    * Remove isolated voxels as final refinement.

* Creation of feature images (all contained within ANTs)
    * Benefits of open source
    * best registration (for template building)
    * Preprocessing
        * Denoising
        * N4 bias correction
    * Types of feature images and motivation for their use (Stage 1)
        * Normalized intensities and neighborhood statistics image
        * Symmetric template --- the brain exhibits a shape and intensity bilateral
          symmetry under normal conditions.  WMHs can "break" this symmetry.
        * Probabilistic segmentations, distance maps and symmetric template indices ---
          help remove false positives
          caused by partial voluming at the gray/white matter interface and the location
          indices since, for example, higher intensities can be found at the periventricular
          caps in normal subjects [@Neema:2009aa] which often confounds automated lesion
          detection algorithms.
    * Types of feature images and motivation for their use (Stage 2)
        * All previously images (for the reasons stated above)
        * ``antsAtroposN4.sh`` with a large prior weight (w=0.5) on all three modalities
          to classify voxels based on intensity (use MRF to smooth out remaining noise
          in labeling).

* Public avail

* Leave one out evaluation strategy overview
    * Create stage 1 feature images for all subjects
    * For each of the 24 subjects, take out a subject and create a Stage 1 random forest
      model from the remaining feature images + manually labeled truth data.
    * For each of the remaining 23 subjects, send them through the Stage 1 RF model.
    * The above step permits the creation of the Stage 2 feature images
    * Create the Stage 2 RF model from the 23 sets of Stage 2 feature images.
    * Send the leave-one-out subject through the two RF models (as described above).
    * Compare with ground truth.

* (Save for Discusion) Difficulties of WMH evaluation (outlined in greater detail here [@MIAreview].
    *
-->

@@

Another popular machine learning technique that has acheieved much success is the
random forest

@@

![Average \texttt{MeanDecreaseAccuracy} plots generated from the creation of all 24 random
forest models for both Stage 1 and Stage 2 during the leave-one-out evaluation.  These plots
are useful in providing a quantitative assessment of the predictive importance of each feature.
The error bars provide the 95^{th} percentile (i.e., $1.96 \times sigma$) and illustrate the
stability of the feature importance across models.](Figures/averageLeaveOneOut.png)

To calculate this quantity for a single feature from a single random forest model, the
decrease in prediction accuracy produced by omitting the specified feature is calculated
during the out-of-bag phase of model creation.

During the out-of-bag error calculation stage of the random forest model creation, the
decrease in prediction accuracy with the omission of a single feature or variable is
tracked and averaged. Those features which have the greatest decrease in mean accuracy are
considered to be the most discriminative. In this work, we do not use these measurements for
feature pruning.
